---
title: "Post-dialysis ema"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: spacelab
---

```{r setup, include=FALSE}
easypackages::libraries("here", "tidyverse", "flexdashboard", 
                        "purrr", "readxl", "gtsummary", 
                        "kableExtra", "scales", "rstatix",
                        "boot", "ggpubr")

source(here("fcn_output.R"))

pds <- read_csv(here::here("pds_alltimepoints.csv"))
```

```{css}
    .chart-shim {
      overflow: auto;
    }
```


# **(Table 1[n=156 pts])** 

## {.tabset .tabset-fade .tabset-pills}
```{r}
post_dial_baseline <- pds |>
  mutate(dialysis_duration =
           strtoi(as.difftime(seconds_to_period(dialysis_stop_time-dialysis_start_time)))/3600,
         `Dialysis Shift` = ifelse(`Dialysis Shift` == "Evening" | 
                                     `Dialysis Shift` == "Midday", 
                                   "Midday or Evening", 
                                   `Dialysis Shift`)) |>
  distinct(id, .keep_all = TRUE) |>
  select(screen_age, gender, race, charlson_tot, vintage_yrs, hb, albumin, 
         opioid_use, antidep_use, antihypertension_use, betablocker_use, 
         fs_imp, psqi_imp, bpi_imp, dep_imp, gad_imp, ssTotal_imp, paTotal_imp, sdi_score, 
         `Dialysis Shift`, dialysis_sched, dialysis_duration, ktv, antihypertension_use,
         betablocker_use)
```

### Table 1
```{r}
post_dial_baseline |>
  tbl_summary(
        statistic = list(all_continuous() ~ "{mean} ({sd})",
                         all_categorical() ~ "{n} ({p}%)"),
        digits = all_continuous() ~ 1,
        missing_text = "(Missing)"
    ) |>
    modify_header(label = "**Variable**") %>%
    bold_labels()
```

### Supplemental table 1
```{r}
post_dial_baseline |>
  tbl_summary(
    by = `Dialysis Shift`,
    statistic = list(all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{n} ({p}%)"),
    digits = all_continuous() ~ 1,
    missing_text = "(Missing)"
    ) |>
  add_p() |>
  modify_header(label = "**Variable**") |>
  bold_labels()
```

### **dialysis vs. non-dialysis controling for cci**

#### Pairwise comparisons

```{r, Mixed-effect models}

library(lme4)
library(broom)
library(broom.mixed)
library(marginaleffects)
library(ggpubr)
library(lmerTest)

fitMod <- function(df, y) {

model_formula <- as.formula(glue::glue("{y} ~ 1 + dialysis_non_first_second + gender + race + 
                                       charlson_tot + screen_age + (1 |id)"))
  
  fitted_model <- lmer(model_formula, data = df, control = lmerControl(optimizer ='bobyqa'))
  
  return(fitted_model)
}


adjMod <- function(ftmdl){
  a <- comparisons(ftmdl
                   ,newdata="marginalmeans",
                   variables="dialysis_non_first_second"
                   ) %>% 
    tidy()
  a
}

```

```{r}
# create a list of the outcome variables
ys <- c("`Negative Mood`", "`Sleepiness/Fatigue`", "`Positive Mood`", "`Alert/Cognitive`")

fits <- ys |>
  map(~ fitMod(pds, .))

names(fits) <- ys

# Get the differences in means
mean_diff <- fits %>% 
  map_dfr(~adjMod(.x)
          ,.id="y"
          ) |>
  mutate(p.value = round(p.value, 3))

# Get the predicted means
# predicted_means <- fits %>% 
#   map_dfr(~predPopMod(.x,tm=c(1,2,3,4))
#           ,.id="y"
#           ) %>% 
#   mutate(Outcome=as.factor(y))
get_overall_p <- function(fits){
  anova(fits) %>% 
    tidy() %>% 
    select(p.value)
}

```

```{r}
mean_diff |>
  select(y, contrast,estimate, p.value, conf.low : conf.high) |>
  mykable(n.left = 2)
```

#### Overall model p-values
```{r}
pds |> 
  pivot_longer(cols = `Negative Mood`:`Alert/Cognitive`, names_to = "CompositeScore") |>
  group_by(CompositeScore, dialysis_non_first_second) |>
  summarise(mean = mean(value, na.rm = TRUE), sd = sd(value, na.rm = TRUE)) |>
  mutate(mean_sd = glue::glue("{round(mean, 1)} ({round(sd, 1)})")) |>
  select(CompositeScore, dialysis_non_first_second, mean_sd) |>
  pivot_wider(names_from = dialysis_non_first_second, values_from = mean_sd) |>
  mykable(n.left = 2)
```


### **Mixed graphs**



#### Figure 2
```{r, fig.align='center', fig.width=12, fig.height=4}
# Create a data frame for the labels
labels_df <- data.frame(
  x = c(2, 6, 10, 14, 18, 22, 26),  # X-coordinates for each day
  y = rep(5.8, 7),                    # Y-coordinate for all labels
  label = c("Day 1 (HD)",
            "Day 2 (Non-HD)",
            "Day 3 (HD)",
            "Day 4 (Non-HD)",
            "Day 5 (HD)", 
            "Day 6 (Non-HD)",
            "Day 7 (Non-HD)"),
  y_min = rep(5.5, 7),
  y_max = rep(5.5, 7),
  group = rep("`Symptom Domain`", 7)
)

diurnal_daily_dialysis_post_dial_ci <- pds |>
    filter(dialysis_order != "NA") |>
    group_by(sequential_time_order) |>
    summarise(across(`Negative Mood`:`Alert/Cognitive`, 
                     list(mean = ~mean(.x, na.rm = TRUE), 
                          sem = ~sd(.x, na.rm = TRUE) / sqrt(sum(!is.na(.x)))), 
                     .names = "{.col}_{.fn}")) |>
    pivot_longer(cols = `Negative Mood_mean`:`Alert/Cognitive_sem`, 
                 names_to = c("Symptom Domain", ".value"), 
                 names_pattern = "(.*)_(.*)") |>
    mutate(
           lower_ci = mean - qt(0.975, df = sum(!is.na(pds$`Negative Mood`)) - 1) * sem,
           upper_ci = mean + qt(0.975, df = sum(!is.na(pds$`Negative Mood`)) - 1) * sem
    ) |>
    ungroup()


posmood_alertcog_trend_post_dial <- diurnal_daily_dialysis_post_dial_ci |>
  filter(`Symptom Domain` %in% c("Alert/Cognitive", "Positive Mood")) |>
  ggplot(aes(x = sequential_time_order, y = mean, ymin=lower_ci, ymax=upper_ci, group=`Symptom Domain`)) +
  geom_ribbon(aes(fill=`Symptom Domain`),alpha = .2) +
  geom_point(size = 2) +
  geom_path(aes(group = `Symptom Domain`, linetype = `Symptom Domain`)) +
  labs(x = "Time of day", y = "Mean Symptom Domain Score") +
  theme_pubr() +
  theme(legend.position = "bottom", 
        legend.text = element_text(size = 11),
        axis.text.x = element_text(hjust = 1, size = 11)) +
  geom_vline(xintercept = c(4, 8, 12, 16, 20, 24, 28), linetype = "dashed", color = "blue") +
  scale_x_continuous(breaks = seq(1:28),
                     label = rep(c("1", "2", "3", "4"), 7)) +
  scale_y_continuous(limits = c(3.85, 5.8)) +
  geom_text(aes(label = format(round(mean, digits=1), nsmall = 1) ), vjust = - 1, hjust = -0.1, size = 4) +
  geom_label(data = labels_df, aes(x = x, y = y, label = label, ymin=y_min, 
                                   ymax=y_max, group = group), 
             size = 4, 
             fill = "white", color = "black", label.padding = unit(0.25, "lines"),
             label.r = unit(0.2, "lines"), label.size = 0.25) +
  scale_linetype_manual(values = c("solid", "dashed")) 

posmood_alertcog_trend_post_dial
#ggsave(here("ema/output/posmood_alertcog_trend.png"), posmood_alertcog_trend, width=12, height=6)
```

#### Figure 1
```{r, fig.align='center', fig.width=12, fig.height=4}
# Create a data frame for the labels
labels_df <- data.frame(
  x = c(2, 6, 10, 14, 18, 22, 26),  # X-coordinates for each day
  y = rep(4.8, 7),                    # Y-coordinate for all labels
  label = c("Day 1 (HD)",
            "Day 2 (Non-HD)",
            "Day 3 (HD)",
            "Day 4 (Non-HD)",
            "Day 5 (HD)", 
            "Day 6 (Non-HD)",
            "Day 7 (Non-HD)"),
  y_min = rep(4.8, 7),
  y_max = rep(4.8, 7),
  group = rep("Sleepiness/Fatigue", 7)
)

negmood_sleepfat_trend_post_dial <- diurnal_daily_dialysis_post_dial_ci |>
  filter(`Symptom Domain` %in% c("Negative Mood", "Sleepiness/Fatigue")) |>
  ggplot(aes(x = sequential_time_order, y = mean, ymin=lower_ci, ymax=upper_ci, group=`Symptom Domain`)) +
  geom_ribbon(aes(fill=`Symptom Domain`),alpha = .2) +
  geom_point(size = 2) +
  geom_path(aes(group = `Symptom Domain`, linetype = `Symptom Domain`)) +
  labs(x = "Time of day", y = "Mean Symptom Domain Score") +
  theme_pubr() +
  theme(legend.position = "bottom", 
        legend.text = element_text(size = 11),
        axis.text.x = element_text(hjust = 1, size = 11)) +
  geom_vline(xintercept = c(4, 8, 12, 16, 20, 24, 28), linetype = "dashed", color = "blue") +
  scale_x_continuous(breaks = seq(1:28),
                     label = rep(c("1", "2", "3", "4"), 7)) +
  scale_y_continuous(limits = c(1.5, 4.8)) +
  geom_text(aes(label = format(round(mean, digits=1), nsmall = 1) ), vjust = - 1, hjust = -0.1, size = 4) +
  geom_label(data = labels_df, aes(x = x, y = y, label = label, ymin=y_min, 
                                   ymax=y_max, group = group), 
             size = 4, 
             fill = "white", color = "black", label.padding = unit(0.25, "lines"),
             label.r = unit(0.2, "lines"), label.size = 0.25) +
  scale_linetype_manual(values = c("solid", "dashed")) 

negmood_sleepfat_trend_post_dial
# ggsave(here("ema/output/negmood_sleepfat_trend.png"), negmood_sleepfat_trend, width=12, height=6)
```


# **Item level analysis**

## {.tabset}

### Supplemental table 2

```{r}
library(lme4)
library(broom)
library(broom.mixed)
library(marginaleffects)
library(ggpubr)
library(lmerTest)

fit_unadjMod <- function(df, y) {

model_formula <- as.formula(glue::glue("{y} ~ dialysis_non_first_second"))
  
  fitted_model <- lm(model_formula, data = df)
  
  return(fitted_model)
}


adjMod_com <- function(ftmdl){
  a <- comparisons(ftmdl
                   ,newdata="marginalmeans",
                   variables="dialysis_non_first_second"
                   ) %>% 
    tidy()
  a
}

adjMod_pred <- function(ftmdl){
  a <- predictions(ftmdl
                   ,newdata="marginalmeans",
                   by="dialysis_non_first_second"
                   ) %>% 
    tidy()
  a
}

```

```{r}
# create a list of the outcome variables
ys <- c("`Negative Mood`", "anxious", "stressed", "tense", "sad", "irritable",
        "`Sleepiness/Fatigue`", "fatigued", "sleepy", "exhausted",
        "`Positive Mood`", "relaxed", "energetic", "calm", "happy", "efficent", 
        "`Alert/Cognitive`", "forgetful", "clear_headed", "concentrated", "effort", "alert")

fits_unadj <- ys |>
  map(~ fit_unadjMod(pds, .))

names(fits_unadj) <- ys

# Get the differences in means
mean_diff_unadj <- fits_unadj %>% 
  map_dfr(~adjMod_com(.x)
          ,.id="y"
          ) |>
  mutate(p.value = round(p.value, 3))

# Get the predicted means
# predicted_means <- fits %>% 
#   map_dfr(~predPopMod(.x,tm=c(1,2,3,4))
#           ,.id="y"
#           ) %>% 
#   mutate(Outcome=as.factor(y))
get_overall_p <- function(fits){
  anova(fits) %>% 
    tidy() %>% 
    select(p.value)
}

```

```{r}
diff_in_mean_unadj <- mean_diff_unadj |>
  select(y, contrast,estimate, p.value, conf.low : conf.high)

diff_in_mean_unadj |>
  DT::datatable(rownames = FALSE, options = list(pageLength = 15, scrollX = TRUE))
```

### Adjusted Analysis

```{r}
fitMod <- function(df, y) {

model_formula <- as.formula(glue::glue("{y} ~ 1 + dialysis_non_first_second + screen_age + charlson_tot + gender + race + (1 |id)"))
  
  fitted_model <- lmer(model_formula, data = df, control = lmerControl(optimizer ='bobyqa'))
  
  return(fitted_model)
}
```

```{r}
# create a list of the outcome variables
ys <- c("`Negative Mood`", "anxious", "stressed", "tense", "sad", "irritable",
        "`Sleepiness/Fatigue`", "fatigued", "sleepy", "exhausted",
        "`Positive Mood`", "relaxed", "energetic", "calm", "happy", "efficent", 
        "`Alert/Cognitive`", "forgetful", "clear_headed", "concentrated", "effort", "alert")

fits <- ys |>
  map(~ fitMod(pds, .))

names(fits) <- ys

# Get the differences in means
mean_diff <- fits %>% 
  map_dfr(~adjMod_com(.x)
          ,.id="y"
          ) |>
  mutate(p.value = round(p.value, 3))

pred <- fits %>% 
  map_dfr(~adjMod_pred(.x)
          ,.id="y"
          )

# Get the predicted means
# predicted_means <- fits %>% 
#   map_dfr(~predPopMod(.x,tm=c(1,2,3,4))
#           ,.id="y"
#           ) %>% 
#   mutate(Outcome=as.factor(y))
get_overall_p <- function(fits){
  anova(fits) %>% 
    tidy() %>% 
    select(p.value)
}

```

```{r}
diff_in_mean <- mean_diff |>
  select(y, contrast,estimate, p.value, conf.low : conf.high)
```

#### Figure 3

```{r}
pred_by_dia <- pred %>% 
  filter(y == "`Negative Mood`" | 
           y == "`Sleepiness/Fatigue`" |
           y == "`Positive Mood`" | 
           y == "`Alert/Cognitive`") %>% select(y, dialysis_non_first_second, estimate) %>%
  reshape2::dcast(y ~ dialysis_non_first_second, value.var = "estimate")
```

```{r}
forest_df <- diff_in_mean %>% 
  filter(y == "`Negative Mood`" | 
           y == "`Sleepiness/Fatigue`" |
           y == "`Positive Mood`" | 
           y == "`Alert/Cognitive`") %>%
  left_join(pred_by_dia, by = "y") %>%
  rename(`Symptom Domain` = y,
         `Post-dialysis` = `Dialysis days`,
         `Non-dialysis` = `Non-dialysis days`) %>%
  mutate(`Symptom Domain` = case_when(`Symptom Domain` == "`Negative Mood`" ~ "Negative Mood",
                             `Symptom Domain` == "`Sleepiness/Fatigue`" ~ "Sleepiness/Fatigue",
                             `Symptom Domain` == "`Positive Mood`" ~ "Positive Mood",
                             TRUE ~ "Alert Cognition       "),
         `Post-dialysis` = round(`Post-dialysis`, 2),
         `Non-dialysis` = round(`Non-dialysis`, 2),
         `Mean Difference (95% CI)` = sprintf("%.2f (%.2f, %.2f)", estimate, conf.low, conf.high),
         ` ` = paste(rep(" ", 50), collapse = ""))
```

```{r}
neg_df <- forest_df %>% 
  filter(`Symptom Domain` == "Negative Mood" | `Symptom Domain` == "Sleepiness/Fatigue")

pos_df <- forest_df %>% 
  filter(`Symptom Domain` == "Positive Mood" | `Symptom Domain` == "Alert Cognition       ")

neg_p <- forestploter::forest(neg_df[,c(1, 7:10)],
                     est = neg_df$estimate,
                     lower = neg_df$conf.low, 
                     upper = neg_df$conf.high,
                     ci_column = 5,
                     ref_line = 0,
                     arrow_lab = c("Post-dialysis is worse", "Better"))

pos_p <- forestploter::forest(pos_df[,c(1, 7:10)],
                     est = pos_df$estimate,
                     lower = pos_df$conf.low, 
                     upper = pos_df$conf.high,
                     ci_column = 5,
                     ref_line = 0,
                     arrow_lab = c("Better", "Post-dialysis is worse"))

# ggsave(here("ema/output/neg_forestplot.png"), neg_p, width=10, height=5)
# ggsave(here("ema/output/pos_forestplot.png"), pos_p, width=10, height=5)
```

```{r}
library(gridExtra)

forest_p <- grid.arrange(neg_p, pos_p, ncol=1)
#ggsave(here("ema/output/forestplot.png"), forest_p, width=10, height=4)
```

#### Table 2
```{r}
f <- factor(c("anxious", "stressed", "tense", "sad", "irritable", "fatigued", "sleepy", "exhausted",
        "relaxed", "energetic", "calm", "happy", "efficent", "forgetful", "clear_headed", 
        "concentrated", "effort", "alert"),
            levels = c("anxious", "stressed", "tense", "sad", "irritable", "fatigued", "sleepy", "exhausted",
        "relaxed", "energetic", "calm", "happy", "efficent", "forgetful", "clear_headed", 
        "concentrated", "effort", "alert"))

pds |> 
  pivot_longer(cols = c("anxious", "stressed", "tense", "sad", "irritable", "fatigued", "sleepy", "exhausted",
        "relaxed", "energetic", "calm", "happy", "efficent", "forgetful", "clear_headed", 
        "concentrated", "effort", "alert"), names_to = "CompositeScore") |>
  group_by(CompositeScore, dialysis_non_first_second) |>
  summarise(mean = mean(value, na.rm = TRUE), sd = sd(value, na.rm = TRUE)) |>
  mutate(mean_sd = glue::glue("{round(mean, 1)} ({round(sd, 1)})")) |>
  select(CompositeScore, dialysis_non_first_second, mean_sd) |>
  pivot_wider(names_from = dialysis_non_first_second, values_from = mean_sd) |>
  left_join(diff_in_mean, by = c("CompositeScore" = "y")) |>
  mykable(n.left = 2) 
```

# **Post-dialysis exacerbation analysis**

## {.tabset .tabset-fade .tabset-pills}


```{r}
# pds stands for post-dialysis syndrome
pds_alltimepoints <- pds |>
  mutate(dialysis_duration = strtoi(as.difftime(seconds_to_period(dialysis_stop_time-dialysis_start_time)))/3600) |>
  rowwise() |>
  mutate("Sleepiness/Fatigue/NegativeMood" = (`Sleepiness/Fatigue` + `Negative Mood`),
         "Alert_Cognitive_Positivemood" = (`Alert/Cognitive` + `Positive Mood`),
         total_symptoms_score = sum(c_across(alert : effort))) |>
  ungroup() |>
  mutate(dialysis_non_first_second = fct_rev(dialysis_non_first_second),
         dialysis_order_collapsed = case_when(
           dialysis_order %in% c("Day 1 (HD)", "Day 2 (Non-HD)") ~ "Day 1",
           dialysis_order %in% c("Day 3 (HD)", "Day 4 (Non-HD)") ~ "Day 2",
           dialysis_order %in% c("Day 5 (HD)", "Day 6 (Non-HD)", "Day 7 (Non-HD)") ~ "Day 3"
         ),
         dialysis_order_collapsed= fct_relevel(dialysis_order_collapsed, 
                                                 "Day 3", 
                                                 "Day 2",
                                                 "Day 1")) 
```


### Unadjusted analyses using mixed-effect model(Supplemental table 3)
```{r}
# create a list of all bivariate combinations of outcome and independent variables
outcome_vars <- c("`Sleepiness/Fatigue/NegativeMood`")
ind_vars_bin <- c("screen_age", "gender", "race", "charlson_tot", "vintage_yrs", "hb",
                  "albumin", "opioid_use", "antidep_use", "fs_imp", "psqi_imp", 
                  "bpi_imp", "dep_imp", "gad_imp", "ssTotal_imp", "paTotal_imp", "sdi_score",
                  "`Dialysis Shift`", "dialysis_sched", "dialysis_duration", "ktv",
                  "cva_yn", "cpd_yn", "diabetes_wo_damage", "antihypertension_use", 
                  "betablocker_use", "dialysis_order_collapsed")

pds_cleaned <- pds_alltimepoints %>% mutate(opioid_use = as.factor(opioid_use),
                              antidep_use = as.factor(antidep_use))

var_combinations_bin <- expand.grid(outcome_vars, ind_vars_bin)

# 
# create a list of linear models for each combination and name the list elements
model_list <- setNames(
  map2(var_combinations_bin$Var1, var_combinations_bin$Var2, function(outcome_var, ind_var) {
    lmer(as.formula(paste(outcome_var, "~", "(" ,  ind_var,
                          ") * dialysis_non_first_second + (1 | id)")), data = pds_cleaned)
  }),
  paste(var_combinations_bin$Var1, var_combinations_bin$Var2, sep = "  vs.  ")
)

# summarize the models using tidy() and store the results in a list
tidy_list <- map(model_list, ~tidy(.x, conf.int = TRUE))

# combine the summary results into a single data frame
summary_df <- bind_rows(tidy_list, .id = "model name") |>
  mutate(across(where(is.numeric), ~ round(., 3))) |>
  filter(term != "(Intercept)") |>
  filter(str_detect(term, ":")) |>
  mutate(`Estimate of Interest`= glue::glue('{estimate} ({conf.low}, {conf.high})')) |>
  select(`model name`, term, `Estimate of Interest`, `p.value`)

DT::datatable(summary_df, options = list(pageLength = 20))
```



```{r, include = FALSE}
outcome_vars <- c("`Sleepiness/Fatigue/NegativeMood`")
ind_vars_bin <- c("vintage_yrs", "hb",
                  "albumin", "opioid_use", "antidep_use", "fs_imp", "psqi_imp", 
                  "bpi_imp", "dep_imp", "gad_imp", "ssTotal_imp", "paTotal_imp", "sdi_score",
                  "`Dialysis Shift`", "dialysis_sched", "dialysis_duration", "ktv",
                  "cva_yn", "cpd_yn", "diabetes_wo_damage", "antihypertension_use", "betablocker_use")

pds_cleaned <- pds %>% mutate(opioid_use = as.factor(opioid_use),
                              antidep_use = as.factor(antidep_use))

var_combinations_bin <- expand.grid(outcome_vars, ind_vars_bin)

# create a list of linear models for each combination and name the list elements
model_list <- setNames(
  map2(var_combinations_bin$Var1, var_combinations_bin$Var2, function(outcome_var, ind_var) {
    lm(as.formula(paste(outcome_var, "~", "screen_age + gender + race + charlson_tot", "+", ind_var)), data = pds_cleaned)
  }),
  paste(var_combinations_bin$Var1, var_combinations_bin$Var2, sep = "  vs.  ")
)

# summarize the models using tidy() and store the results in a list
tidy_list <- map(model_list, ~tidy(.x, conf.int = TRUE))

output <- bind_rows(tidy_list, .id = "model name") |>
  mutate(across(where(is.numeric), ~ round(., 4))) |>
  filter(!term %in% c("(Intercept)", "screen_age", "genderMale", "raceOthers", 
                      "charlson_tot", 'raceWhite')) |>
  mutate(`Estimate of Interest`= glue::glue('{estimate} ({conf.low}, {conf.high})')) |>
  select(`model name`, term, `Estimate of Interest`, `p.value`)

DT::datatable(output, options = list(pageLength = 20))
  
```


```{r, include = FALSE}
outcome_vars <- c("`Sleepiness/Fatigue/NegativeMood`")
ind_vars_bin <- c("vintage_yrs", "hb",
                  "albumin", "opioid_use", "antidep_use", "fs_imp", "psqi_imp", 
                  "bpi_imp", "dep_imp", "gad_imp", "ssTotal_imp", "paTotal_imp", "sdi_score",
                  "`Dialysis Shift`", "dialysis_sched", "dialysis_duration", "ktv",
                  "antihypertension_use", "betablocker_use")

pds_cleaned <- pds %>% mutate(opioid_use = as.factor(opioid_use),
                              antidep_use = as.factor(antidep_use))

var_combinations_bin <- expand.grid(outcome_vars, ind_vars_bin)

# create a list of linear models for each combination and name the list elements
model_list <- setNames(
  map2(var_combinations_bin$Var1, var_combinations_bin$Var2, function(outcome_var, ind_var) {
    lm(as.formula(paste(outcome_var, "~", "screen_age + gender + race + cva_yn + cpd_yn + diabetes_wo_damage", "+", ind_var)), data = pds_cleaned)
  }),
  paste(var_combinations_bin$Var1, var_combinations_bin$Var2, sep = "  vs.  ")
)

# summarize the models using tidy() and store the results in a list
tidy_list <- map(model_list, ~tidy(.x, conf.int = TRUE))

output <- bind_rows(tidy_list, .id = "model name") |>
  mutate(across(where(is.numeric), ~ round(., 4))) |>
  filter(!term %in% c("(Intercept)", "screen_age", "genderMale", "raceOthers", 
                      "cva_yn1", "cpd_yn1", "diabetes_wo_damage1", 'raceWhite')) |>
  mutate(`Estimate of Interest`= glue::glue('{estimate} ({conf.low}, {conf.high})')) |>
  select(`model name`, term, `Estimate of Interest`, `p.value`)

DT::datatable(output, options = list(pageLength = 20))
  
```

### Table 3

Age, gender, race, and cci
```{r}
fit_controllers_mixed_model <- lmer(data = pds_alltimepoints, `Sleepiness/Fatigue/NegativeMood` ~ (screen_age + gender + race + charlson_tot) * dialysis_non_first_second + (1 | id))

fit_controllers_mixed_model_results <- fit_controllers_mixed_model |> 
  tidy(conf.int = T) |> 
  filter(str_detect(term, ":")) |>
  mutate(across(where(is.numeric), ~ round(., 4))) |>
  mutate(`Estimate of Interest`= glue::glue('{estimate} ({conf.low}, {conf.high})')) |>
  select(term, `Estimate of Interest`, p.value) 

kable(fit_controllers_mixed_model_results)
```

```{r}
outcome_vars <- c("`Sleepiness/Fatigue/NegativeMood`")
ind_vars_bin <- c("vintage_yrs", "hb",
                  "albumin", "opioid_use", "antidep_use", "fs_imp", "psqi_imp", 
                  "bpi_imp", "dep_imp", "gad_imp", "ssTotal_imp", "paTotal_imp", "sdi_score",
                  "`Dialysis Shift`", "dialysis_sched", "dialysis_duration", "ktv",
                  "cva_yn", "cpd_yn", "diabetes_wo_damage", "antihypertension_use", 
                  "betablocker_use", "dialysis_order_collapsed")

pds_cleaned <- pds_alltimepoints %>% mutate(opioid_use = as.factor(opioid_use),
                              antidep_use = as.factor(antidep_use))

var_combinations_bin <- expand.grid(outcome_vars, ind_vars_bin)

# create a list of linear models for each combination and name the list elements
model_list <- setNames(
  map2(var_combinations_bin$Var1, var_combinations_bin$Var2, function(outcome_var, ind_var) {
    lmer(as.formula(paste(outcome_var, "~", "(" ,"screen_age + gender + race + charlson_tot", "+", ind_var,
                          ") * dialysis_non_first_second + (1 | id)")), data = pds_cleaned)
  }),
  paste(var_combinations_bin$Var1, var_combinations_bin$Var2, sep = "  vs.  ")
)

# summarize the models using tidy() and store the results in a list
tidy_list <- map(model_list, ~tidy(.x, conf.int = TRUE))

output <- bind_rows(tidy_list, .id = "model name") |>
  mutate(across(where(is.numeric), ~ round(., 4))) |>
  filter(str_detect(term, ":")) |>
  filter(! (str_starts(term, "screen_age:"))) |>
  filter(! (str_starts(term, "genderMale:"))) |>
  filter(! (str_starts(term, "raceOthers:"))) |>
  filter(! (str_starts(term, "raceWhite:"))) |>
  filter(! (str_starts(term, "charlson_tot:"))) |>
  filter(! (str_starts(term, "fs_imp:"))) |>
  mutate(`Estimate of Interest`= glue::glue('{estimate} ({conf.low}, {conf.high})')) |>
  select(`model name`, term, `Estimate of Interest`, `p.value`)

DT::datatable(output, options = list(pageLength = 20))
  
```
